Lipids and dementia\\ An investigation of their relationship

### 2020-02-19 01-Chp1-Introduction.Rmd
Major updates
Updates
Add word count
Major changes

This is a test of the bibliography (@Darwin1859)

>>>>

## Aims and Objectives of the thesis

### Aim

### Objective

## Chapter Overview

* Chapter \@ref(sys-rev-heading)
* Chapter \@ref(chapter-3-heading)
* Chapter \@ref(chapter-3-heading)

## Thesis Output

### Peer reviewed papers

### Papers under review

### Software

* `robvis`: An R package and associted `shiny` web application that allows users to easily visualise the results of risk of bias graphs.

* `medrxvir`: An R package

### Talks

## Summary

*
* 
*

### 2020-02-19 03-Ch3-CPRD-Analysis.Rmd
Major changes

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:chapter2-quote)'}
A straight line may be the shortest distance between two points, but it is by no means the most interesting
```
(ref:chapter2-quote) --- Third Doctor

@@

One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(chapter-2-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.

@@

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:chapter2-quote)'}
"When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin"
```
(ref:chapter2-quote) --- Harold F. Dorn, 1953 [@dorn1953]

@@

One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.

@@

However, this is not the case. Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event. Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modifcation is ineffective/inappropriate, should recieved a lipid regulation agent. However, this analysis could not find any effect of QRISK2 scores on statins precription levels at 6 months. [Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months. Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that acutally did what they should.]

As expected, in a confirmatory analysis using lipid levels, there was no association between <span color="red">the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, incdicating that adjusting for this variable was not required. *</span>

### 2020-02-19 _00-introduction.Rmd
Major changes

# Covering material {-}

@@

words01 <- as.numeric(wordcountaddin::word_count("01-Chp1-Introduction.Rmd"))
words02 <- as.numeric(wordcountaddin::word_count("02-Chp2-Systematic-Review.Rmd"))
words03 <- as.numeric(wordcountaddin::word_count("03-Ch3-CPRD-Analysis.Rmd"))

words <- words01 + words02 + words03

>>>>

# Preface {-}

@@

words01 <- as.numeric(wordcountaddin::word_count("01-Chp1-Introduction.Rmd"))
words02 <- as.numeric(wordcountaddin::word_count("02-Chp2-Systematic-Review.Rmd"))
words03 <- as.numeric(wordcountaddin::word_count("03-Ch3-CPRD-Analysis.Rmd"))
words04 <- as.numeric(wordcountaddin::word_count("011-Chp2-Background.Rmd"))
words05 <- as.numeric(wordcountaddin::word_count("012-Chp-Systematic-Review-Tools.Rmd"))
words06 <- as.numeric(wordcountaddin::word_count("20-Discussion.Rmd"))

words <- words01 + words02 + words03 + words04 + words05 + words06

### 2020-02-19 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
Major changes

% UL 1 Dec 2018, fix to include code in shaded environments

@@

% all your chapters and appendices will appear here
\hypertarget{covering-material}{%
\chapter*{Covering material}\label{covering-material}}
\addcontentsline{toc}{chapter}{Covering material}

@@

\begin{itemize}
\item
  Word count: 1751 words
\item
  Change since last day: 0 words
\item
  Days: 5 days
\item
  Words per day: 350.2
\end{itemize}

\includegraphics{_main_files/figure-latex/unnamed-chunk-4-1.pdf}

@@

\begin{itemize}
\tightlist
\item
  Chapter \ref{chapter-2-heading}
\item
  Chapter \ref{chapter-3-heading}
\item
  Chapter \ref{chapter-3-heading}
\end{itemize}

@@

@@

\begin{savequote}
Hold
\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-chang2012}{1}}}\end{savequote}

\hypertarget{chapter-2-heading}{%
\chapter{Chapter 2: Systematic Review}\label{chapter-2-heading}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.~(2016).\textsuperscript{\protect\hyperlink{ref-bramer2016}{2}} Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.\textsuperscript{\protect\hyperlink{ref-ouzzani2016}{3}}
Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria. If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
Full-text screening will also be completed in full by the primary author. A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage will be recorded. Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague. A PRIMSA flow diagram will be produced to document how records moved through the review.\textsuperscript{\protect\hyperlink{ref-zotero-766}{4}}

@@

Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.~an adapted version of the Petersen criteria\textsuperscript{\protect\hyperlink{ref-petersen1999}{5}}) and create ordinal groups of patients (e.g.~no dementia or dementia/MCI/dementia) based on this definition.

@@

Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design. Randomised controlled trials were assessed using the RoB2 tool,\textsuperscript{\protect\hyperlink{ref-sterne2019}{6}}, non-randomised studies of interventions were assessed using the ROBINS-I tool,\textsuperscript{\protect\hyperlink{ref-sterne2016}{7}} and non-randomised studies of exposures were assessed using the ROBINS-E tool.{[}TBC{]}

@@

\begin{savequote}
A straight line may be the shortest distance between two points, but it
is by no means the most interesting
\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-chang2012}{1}}}\end{savequote}

\hypertarget{chapter-3-analysis-of-the-relationship-between-lipid-regulating-agent-use-and-dementia-outcomes-in-the-clinical-practice-research-datalink}{%
\chapter{Chapter 3: Analysis of the relationship between lipid regulating agent use and dementia outcomes in the Clinical Practice Research Datalink}\label{chapter-3-analysis-of-the-relationship-between-lipid-regulating-agent-use-and-dementia-outcomes-in-the-clinical-practice-research-datalink}}

@@

One of the problems I'll point out with the trials in the systematic review chapter (Chapter \ref{chapter-2-heading}) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.

@@

@@

\emph{No CVD (t=0) -\textgreater{} No LRA (t=0) -\textgreater{} CVD (t=1) -\textgreater{} LRA (t=1) -\textgreater{} Dementia (t=2)}

@@

i.e.
Timepoint 12345678
CVD 00001111
Treatment 00000111

@@

@@

\hypertarget{list-of-one-thing}{%
\chapter{List of one thing}\label{list-of-one-thing}}

\hypertarget{list-of-something-else}{%
\chapter{List of something else}\label{list-of-something-else}}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-chang2012}{}%
1. Chang, C.-C. H., Zhao, Y., Lee, C.-W. \& Ganguli, M. Smoking, death, and Alzheimer's disease: A case of competing risks. \emph{Alzheimer Disease and Associated Disorders} \textbf{26}, 300--306 (2012).

\leavevmode\hypertarget{ref-bramer2016}{}%
2. Bramer, W. M., Giustini, D., de Jonge, G. B., Holland, L. \& Bekhuis, T. De-duplication of database search results for systematic reviews in EndNote. \emph{Journal of the Medical Library Association : JMLA} \textbf{104}, 240--243 (2016).

\leavevmode\hypertarget{ref-ouzzani2016}{}%
3. Ouzzani, M., Hammady, H., Fedorowicz, Z. \& Elmagarmid, A. Rayyan-a web and mobile app for systematic reviews. \emph{Systematic Reviews} \textbf{5}, 210 (2016).

\leavevmode\hypertarget{ref-zotero-766}{}%
4. The PRISMA statement for reporting systematic reviews and meta-analyses of studies that evaluate healthcare interventions: Explanation and elaboration \textbar{} The BMJ.

\leavevmode\hypertarget{ref-petersen1999}{}%
5. Petersen, R. C. \emph{et al.} Mild cognitive impairment: Clinical characterization and outcome. \emph{Archives of Neurology} \textbf{56}, 303--308 (1999).

\leavevmode\hypertarget{ref-sterne2019}{}%
6. Sterne, J. A. C. \emph{et al.} RoB 2: A revised tool for assessing risk of bias in randomised trials. \emph{BMJ} \textbf{366}, (2019).

\leavevmode\hypertarget{ref-sterne2016}{}%
7. Sterne, J. A. \emph{et al.} ROBINS-I: A tool for assessing risk of bias in non-randomised studies of interventions. \emph{BMJ} \textbf{355}, (2016).

>>>>

% UL 1 Dec 2018, fix to include code in shaded environments
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
%UL 2 Dec 2018 add a bit of white space before and after code blocks
\renewenvironment{Shaded}
{
  \vspace{4pt}%
  \begin{snugshade}%
}{%
  \end{snugshade}%
  \vspace{4pt}%
}

@@

% all your chapters and appendices will appear here
\hypertarget{preface}{%
\chapter*{Preface}\label{preface}}
\addcontentsline{toc}{chapter}{Preface}

@@

\begin{itemize}
\item
  Word count: 2544 words
\item
  Change since last day: 0 words
\item
  Days: 13 days
\item
  Words per day: 195.6923077
\end{itemize}

\includegraphics{_main_files/figure-latex/unnamed-chunk-14-1.pdf}

@@

\begin{itemize}
\tightlist
\item
  Chapter \ref{sys-rev-heading}
\item
  Chapter \ref{chapter-3-heading}
\item
  Chapter \ref{chapter-3-heading}
\end{itemize}

@@

\begin{itemize}
\item
  \texttt{robvis}: An R package and associted \texttt{shiny} web application that allows users to easily visualise the results of risk of bias graphs.
\item
  \texttt{medrxvir}: An R package
\end{itemize}

@@

\hypertarget{background}{%
\chapter{Background}\label{background}}

\hypertarget{dementia}{%
\section{Dementia}\label{dementia}}

\hypertarget{history}{%
\subsection{History}\label{history}}

\hypertarget{economic-impact}{%
\subsection{Economic impact}\label{economic-impact}}

\hypertarget{risk-factors}{%
\subsection{Risk factors}\label{risk-factors}}

\hypertarget{treatments}{%
\subsection{Treatments}\label{treatments}}

\hypertarget{preventative-measures}{%
\subsection{Preventative measures}\label{preventative-measures}}

\hypertarget{serum-lipids}{%
\section{Serum lipids}\label{serum-lipids}}

\hypertarget{range-of-lipids}{%
\subsection{Range of lipids}\label{range-of-lipids}}

\hypertarget{hdl-c}{%
\subsection{HDL-c}\label{hdl-c}}

\hypertarget{ldl-c}{%
\subsection{LDL-c}\label{ldl-c}}

\hypertarget{triglycerides}{%
\subsection{Triglycerides}\label{triglycerides}}

\hypertarget{total-cholesterol}{%
\subsection{Total cholesterol}\label{total-cholesterol}}

\hypertarget{summary-1}{%
\section{Summary}\label{summary-1}}

\begin{savequote}
Why are open source statistical programming\\
languages the best?

Because they R.
\qauthor{--- Bealy, 2013\textsuperscript{\protect\hyperlink{ref-bealy2013}{1}}}\end{savequote}

\hypertarget{creating-new-systematic-review-tools-in-r}{%
\chapter{Creating new systematic review tools in R}\label{creating-new-systematic-review-tools-in-r}}

\hypertarget{background-1}{%
\section{Background}\label{background-1}}

R is a pro
Below I introduce two R packages that I created to faciliate some aspects of the systematic review process.

\hypertarget{robvis}{%
\section{\texorpdfstring{\texttt{robvis}}{robvis}}\label{robvis}}

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

\hypertarget{installation}{%
\subsection{Installation}\label{installation}}

A stable version of \texttt{robvis} is hosted on the Comprehensive R Archive Network (CRAN) and can be installed using:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"robvis"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

As development of \texttt{robvis} is ongoing, new features are often available in the development version some time before they appear in the stable CRAN version. The most recent development version can be install from GitHub using:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"mcguinlu/robvis"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{reception-and-future-plans}{%
\subsection{Reception and Future Plans}\label{reception-and-future-plans}}

As of 19 February, 2020, \texttt{robvis} has been downloaded more than 1200 times. It has been accepted

It has also been intergrated with a suite of new online platforms for performing risk of bias assessments online.

In this thesis, \texttt{robvis} is used to present the results of the risk of bias assessments conducted as part of the systematic review and

While \texttt{robvis} currently provides a stable, future development work is planned.

\hypertarget{medrxivr}{%
\section{\texorpdfstring{\texttt{medrxivr}}{medrxivr}}\label{medrxivr}}

\hypertarget{introduction-1}{%
\subsection{Introduction}\label{introduction-1}}

Searching pre-print repositories is becoming an increasingly important part of a systematic review. However, while several of the main repositories (e.g.~arXiv, bioRxiv) have existing methods by which records can be searched and downloaded en masse, this is not true for medRxiv, an offspring of bioRxiv which hosts preprints in the medical, clinical, and related health sciences.

At present, medRxiv allows only simple search queries, as opposed to the often complex boolean logic that information specialists use to query other major databases. Additionally, record details must be downloaded individually, rather than in batches, making the export of relevant records for title and abstract screening a time consuming task.

Im order to facilitate the searching

\hypertarget{installation-1}{%
\subsection{Installation}\label{installation-1}}

To install \texttt{medrxivr} from CRAN:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Currently doesn't work as not on CRAN}

\KeywordTok{install.packages}\NormalTok{(}\StringTok{"medrxivr"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

To install the development version from GitHub:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"mcguinlu/medrxivr"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

The \texttt{medrxivr} project is split into two parts:

\begin{itemize}
\tightlist
\item
  A webscraper that runs once a day which collects and cleans new records uploaded to medRxiv, and adds them to a machine readable database.
\item
  A lightweight R package that provides an interface for this database, allowing users to search for relevant records, and easily retieve the associated full tex PDFs.
\end{itemize}

The webscraper is a straightforward R script built in R using \texttt{rvest}{[}cite{]} and a range of text processing packages{[}cite{]}. To quickly illustrate the process, the code to retrieve the total number of records on medRxiv is included below:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Include and highly comment code. }
\end{Highlighting}
\end{Shaded}

Using Windows Task Scheduler, the script is scheduled to automatically run every morning, adding new records uploaded to medRxiv since the last run of the webscraper to a local comma-seperated-values (CSV) file. Following quality control checks, the updated dataset is automatically uploaded to a cloud server, and immediately becomes available to the main \texttt{medrxivr} package functions.

The functions in the \texttt{medrxivr} package then facilitate users in working with this dataset. There are two main functions and a helper function:

\begin{itemize}
\tightlist
\item
  \texttt{mx\_search()} {[}main{]}: Enables users to search the medrxivr data dump, using regular expressions and boolean logic.
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{topic1  <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"dementia"}\NormalTok{,}\StringTok{"vascular"}\NormalTok{,}\StringTok{"alzheimer's"}\NormalTok{)  }\CommentTok{# Combined with OR}
\NormalTok{topic2  <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"lipids"}\NormalTok{,}\StringTok{"statins"}\NormalTok{,}\StringTok{"cholesterol"}\NormalTok{)     }\CommentTok{# Combined with OR}

\NormalTok{myquery <-}\StringTok{ }\KeywordTok{list}\NormalTok{(topic1, topic2)                    }\CommentTok{# Combined with AND}

\NormalTok{results <-}\StringTok{ }\KeywordTok{mx_search}\NormalTok{(myquery)}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\tightlist
\item
  \texttt{mx\_download()} {[}main{]}: Takes the output from \texttt{mx\_search()} and retrieves the full text PDF for each record, saving it to a folder specified by the user.
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{mx_download}\NormalTok{(results,        }\CommentTok{# Object returned by mx_search}
            \StringTok{"pdf/"}\NormalTok{)         }\CommentTok{# Directory to save PDFs to }
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\tightlist
\item
  \texttt{mx\_crosscheck()} {[}helper{]}: Provides information on the version of the data dump that the user is searching, and checks whether any new records have been uploaded to medRxiv since the last run of the webscraper.
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{mx_crosscheck}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Using medRxiv DataDump - 2020-02-19 10:38
\end{verbatim}

\begin{verbatim}
## 2 new record(s) added to medRxiv since last data dump
\end{verbatim}

\hypertarget{reception-and-future-plans-1}{%
\subsection{Reception and Future Plans}\label{reception-and-future-plans-1}}

\texttt{medrxivr}

Published paper,

\hypertarget{dicussion}{%
\section{Dicussion}\label{dicussion}}

\hypertarget{summary-2}{%
\section{Summary}\label{summary-2}}

*In this Chapter, I have introduced two new tools for facilitating evidence syntheses in R: \texttt{robvis} and \texttt{medrxivr}

\begin{itemize}
\item
  I have
\item
  The impact of these packages to date, and a roadmap for their future development, has been discussed.
\end{itemize}

\begin{savequote}
Hold
\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-chang2012}{2}}}\end{savequote}

\hypertarget{sys-rev-heading}{%
\chapter{Chapter 2: Systematic Review}\label{sys-rev-heading}}

@@

@@

Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.~(2016).\textsuperscript{\protect\hyperlink{ref-bramer2016}{3}} Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.\textsuperscript{\protect\hyperlink{ref-ouzzani2016}{4}}
Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria. If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
Full-text screening will also be completed in full by the primary author. A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage will be recorded. Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague. A PRIMSA flow diagram will be produced to document how records moved through the review.\textsuperscript{\protect\hyperlink{ref-zotero-766}{5}}

@@

Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.~an adapted version of the Petersen criteria\textsuperscript{\protect\hyperlink{ref-petersen1999}{6}}) and create ordinal groups of patients (e.g.~no dementia or dementia/MCI/dementia) based on this definition.

@@

Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design. Randomised controlled trials were assessed using the RoB2 tool,\textsuperscript{\protect\hyperlink{ref-sterne2019}{7}}, non-randomised studies of interventions were assessed using the ROBINS-I tool,\textsuperscript{\protect\hyperlink{ref-sterne2016}{8}} and non-randomised studies of exposures were assessed using the ROBINS-E tool.{[}TBC{]}

@@

\begin{savequote}
``When dealing with human beings controlled experiments frequently prove
to be impracticable, so for a scientific basis for our assumptions we
turn to past history to reconstruct the suspected causal chain of events
- and then our statistical troubles may begin''
\qauthor{--- Harold F. Dorn, 1953\textsuperscript{\protect\hyperlink{ref-dorn1953}{9}}}\end{savequote}

\hypertarget{chapter-3-primary-analysis-of-lipid-regulating-agents-and-dementia}{%
\chapter{Chapter 3: Primary analysis of lipid regulating agents and dementia}\label{chapter-3-primary-analysis-of-lipid-regulating-agents-and-dementia}}

@@

One of the problems I'll point out with the trials in the systematic review chapter (Chapter \ref{sys-rev-heading}) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.

@@

\hypertarget{methods-2}{%
\section{Methods}\label{methods-2}}

@@

\begin{verbatim}
_No CVD (t=0) -> No LRA (t=0) -> CVD (t=1) -> LRA (t=1) -> Dementia (t=2)_
\end{verbatim}

@@

i.e.\\
Timepoint 12345678\\
CVD 00001111\\
Treatment 00000111

@@

However, this is not the case. Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,\textsuperscript{\protect\hyperlink{ref-hippisley-cox2008}{10}} which estimates a patients' 10-year risk of a cardiovascular event. Current NICE guidelines state that those with a QRISK score of 10\% or higher, and in whom lifestyle modifcation is ineffective/inappropriate, should recieved a lipid regulation agent. However, this analysis could not find any effect of QRISK2 scores on statins precription levels at 6 months. {[}Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months. Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that acutally did what they should.{]}

As expected, in a confirmatory analysis using lipid levels, there was no association between the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, incdicating that adjusting for this variable was not required. *

\hypertarget{references}{%
\chapter{References}\label{references}}

@@

\hypertarget{by-chapter}{%
\chapter{By Chapter}\label{by-chapter}}

\hypertarget{chapter-1}{%
\section{Chapter 1}\label{chapter-1}}

\hypertarget{chapter-2}{%
\section{Chapter 2}\label{chapter-2}}

\hypertarget{other-appendix}{%
\chapter{Other Appendix}\label{other-appendix}}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-bealy2013}{}%
1. Bealy, C. R Programming Humour. \emph{Cross Validated} (2013).

\leavevmode\hypertarget{ref-chang2012}{}%
2. Chang, C.-C. H., Zhao, Y., Lee, C.-W. \& Ganguli, M. Smoking, death, and Alzheimer's disease: A case of competing risks. \emph{Alzheimer Disease and Associated Disorders} \textbf{26}, 300--306 (2012).

\leavevmode\hypertarget{ref-bramer2016}{}%
3. Bramer, W. M., Giustini, D., de Jonge, G. B., Holland, L. \& Bekhuis, T. De-duplication of database search results for systematic reviews in EndNote. \emph{Journal of the Medical Library Association : JMLA} \textbf{104}, 240--243 (2016).

\leavevmode\hypertarget{ref-ouzzani2016}{}%
4. Ouzzani, M., Hammady, H., Fedorowicz, Z. \& Elmagarmid, A. Rayyan-a web and mobile app for systematic reviews. \emph{Systematic Reviews} \textbf{5}, 210 (2016).

\leavevmode\hypertarget{ref-zotero-766}{}%
5. The PRISMA statement for reporting systematic reviews and meta-analyses of studies that evaluate healthcare interventions: Explanation and elaboration \textbar{} The BMJ.

\leavevmode\hypertarget{ref-petersen1999}{}%
6. Petersen, R. C. \emph{et al.} Mild cognitive impairment: Clinical characterization and outcome. \emph{Archives of Neurology} \textbf{56}, 303--308 (1999).

\leavevmode\hypertarget{ref-sterne2019}{}%
7. Sterne, J. A. C. \emph{et al.} RoB 2: A revised tool for assessing risk of bias in randomised trials. \emph{BMJ} \textbf{366}, (2019).

\leavevmode\hypertarget{ref-sterne2016}{}%
8. Sterne, J. A. \emph{et al.} ROBINS-I: A tool for assessing risk of bias in non-randomised studies of interventions. \emph{BMJ} \textbf{355}, (2016).

\leavevmode\hypertarget{ref-dorn1953}{}%
9. Dorn, H. F. Philosophy of Inferences from Retrospective Studies. \emph{American Journal of Public Health and the Nations Health} \textbf{43}, 677--683 (1953).

\leavevmode\hypertarget{ref-hippisley-cox2008}{}%
10. Hippisley-Cox, J. \emph{et al.} Predicting cardiovascular risk in England and Wales: Prospective derivation and validation of QRISK2. \emph{BMJ} \textbf{336}, 1475--1482 (2008).
